%% 
%% ACM LaTeX Template for:
%% ACM Transactions on Economics and Computation (TEAC)
%%
\documentclass[acmsmall]{acmart}

%% Packages
\usepackage{booktabs}% Elegant tables
\usepackage{algorithm}% Algorithm wrapper
\usepackage{algorithmicx}% Algorithmic tools
\usepackage{algpseudocode}% Pseudocode layouts
\usepackage{listings}% Code listing formatting

%% Configure figures path
\graphicspath{{figures/}}

%% Journal & copyright settings (placeholders for camera-ready, standard for draft/review)
\setcopyright{acmcopyright}
\copyrightyear{2026}
\acmYear{2026}
\acmDOI{}
\acmJournal{TEAC}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmMonth{1}

%% Mathematical notation shortcuts
\newcommand{\E}{\mathbb{E}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

%% Theorem-like environments
\newtheorem{remark}{Remark}
\newtheorem{assumption}{Assumption}

%% Custom macros for Strategic Feature Withholding
\newcommand{\bV}{b_{\mathrm{V}}} % OLS estimator
\newcommand{\bS}{b_{\mathrm{S}}} % Strategic optimal estimator
\newcommand{\RV}{R_{\mathrm{V}}} % Vanilla/Mandatory risk
\newcommand{\RS}{R_{\mathrm{S}}} % Strategic risk
\newcommand{\bhatV}{\hat{b}_{\mathrm{V}}} % Empirical vanilla
\newcommand{\bhatS}{\hat{b}_{\mathrm{S}}} % Empirical strategic
\newcommand{\RhatV}{\hat{R}_{\mathrm{V}}} % Empirical vanilla risk
\newcommand{\RhatS}{\hat{R}_{\mathrm{S}}} % Empirical strategic risk
\newcommand{\ip}[2]{\langle #1, #2 \rangle} % Inner product
\newcommand{\phiSurr}{\phi_{\mathrm{surr}}} % Surrogate loss
\newcommand{\PiW}{\Pi_{\mathcal{W}}} % Projection operator
\newcommand{\I}[1]{\mathbf{1}\{#1\}} % Indicator function
\newcommand{\Ept}[1]{\mathbb{E}_{#1}} % Expectation with subscript
\newcommand{\cO}{\mathcal{O}} % Big-O notation
\newcommand{\cK}{\mathcal{K}} % Class size set
\newcommand{\ThetaS}{\Theta_{\mathrm{S}}} % Strategic classification weights

\begin{document}

\title[Voluntary Feature Revelation]{Voluntary Feature Revelation in Predictive Tasks: A Unified Framework for Regression and Multiclass Classification}

%% Authors and Affiliations
\author{Manish Kumar Singh}
\email{corresponding.author@email.com}
\affiliation{%
  \institution{Indian Institute of Technology Bombay}
  \department{Centre for Systems and Control}
  \city{Mumbai}
  \state{Maharashtra}
  \country{India}
}

\author{Ankur A. Kulkarni}
\email{second.author@email.com}
\affiliation{%
  \institution{Indian Institute of Technology Bombay}
  \department{Centre for Systems and Control}
  \city{Mumbai}
  \state{Maharashtra}
  \country{India}
}

\author{Kriti Mahajan}
\email{third.author@email.com}
\affiliation{%
  \institution{Amazon India}
  \city{Bangalore}
  \state{Karnataka}
  \country{India}
}

\begin{abstract}
We investigate the framework of machine learning in the presence of strategic information disclosure, specifically focusing on the problem of voluntary feature revelation. This scenario is modeled as a Stackelberg game: a data provider (the sender) strategically determines whether to reveal or withhold optional features to optimize their individual payoff, while a decision-maker (the receiver) commits to a predictive model designed to minimize strategic prediction error. We analyze this interaction across two fundamental prediction spaces: continuous labels (regression) and discrete labels (multiclass classification). For both settings, we examine three sequential regimes of interaction: (i) the decision-theoretic game foundations, establishing necessary and sufficient conditions under which voluntary disclosure benefits the receiver; (ii) the offline batch learning problem, deriving uniform generalization bounds and sample complexity rates under finite training data; and (iii) the online learning problem, designing algorithms to learn under partial or bandit feedback in real-time. Since optimizing the discontinuous, step-like strategic risk is computationally intractable (NP-hard), we leverage smooth surrogate loss formulations to construct gradient-based optimization routines with rigorous regret guarantees—proving $O(\sqrt{T})$ regret for regression and $O(T^{2/3})$ expected regret for classification. Our theoretical findings are validated through comprehensive simulations, mapping out strategic advantage regions and confirming the empirical convergence rates under varying environment dynamics.
\end{abstract}

\keywords{Strategic Machine Learning, Voluntary Disclosure, Stackelberg Games, Sample Complexity, Online Regret, Surrogate Loss}

\maketitle

%% Section 1: Introduction & Related Work
\input{sections/1_introduction.tex}

%% Section 2: Unified Problem Formulation
\input{sections/2_formulation.tex}

%% Section 3: Regression under Strategic Withholding
\input{sections/3_regression.tex}

%% Section 4: Multiclass Classification under Strategic Withholding
\input{sections/4_classification.tex}

%% Section 5: Simulation Results & Empirical Validation
\input{sections/5_experiments.tex}

%% Section 6: Conclusion and Future Work
\input{sections/6_conclusion.tex}

%% Section 7: Postponed Proofs
\input{sections/7_postponed_proofs.tex}

%% Declarations & Acknowledgments
\begin{acks}
The authors thank the members of the Systems and Control group at IIT Bombay for
stimulating discussions on mechanism design and strategic learning. The authors
also thank the anonymous reviewers whose comments substantially improved the
presentation of this work.

\paragraph{Generative AI Disclosure.}
The authors acknowledge the use of AI-assisted writing and code-generation tools
(including large language models) in preparing drafts of mathematical proofs,
code outlines, and paper skeletons. All mathematical claims, theorems, and proofs
have been independently verified by the authors. This disclosure is made in
compliance with ACM's guidelines on the use of generative AI in scholarly
publication.
\end{acks}

\section*{Funding Statement}
This research was conducted as part of the doctoral programme at the Centre for
Systems and Control, Indian Institute of Technology Bombay. No dedicated external
grant funding was received for this specific study. The research infrastructure
was supported by the Indian Institute of Technology Bombay.

\section*{Competing Interests}
The authors declare that they have no competing financial or personal interests
that could have appeared to influence the work reported in this paper.

%% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
